animbook: Visualizing changes in performance measures and demographic affiliations using animation

### 2023-10-02 animbook-journal.Rmd
structure of paper

---
title: "animbook: An R Package for Visualize ..."
date: 04/09/2023
abstract: >
  An abstract of less than 150 words.
draft: true
author:  
  - name: Krisanat Anukarnsakulchularp
    affiliation: Monash University
    address:
    - Faculty of Business and Economics
    - Melbourne, Australia
    orcid: 0009-0008-5638-7124
    email:  kanu0003@student.monash.edu
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: animbook-journal.bib

@@

# Problem and data characterization

To look for the flow between group, one of the most common tools we look at is sankey chart. It represent the movement of the values from one set to another. However, with the static sankey, the only information presented are what is the proportion of the movement, and which states the quantities move to, this often enough in explaining the flow and helps making the decision necessary. To present more information, color could be used to represent the demographic of the group. What if the information that are interesting lies in the times domain, how could the plot captured that information?

@@

The osiris data from Bureau van Dijk, contains an information on listed, and major unlisted/delisted companies across the world. This is one of an example of accounting data, where the objective is to observed the movement of the company between the quantile and how japan companies are ranked compared to others.

# Operation and data type abstraction

@@

# Visualization and interaction design

# Package design

@@

# Package Usage

## Data preprocesing step

@@

>>>>

---
title: "animbook: Visualizing changes in performance measures and demographic affiliations using animation"
date: 04/09/2023
abstract: >
  An abstract of less than 150 words.
draft: true
author:  
  - name: Krisanat Anukarnsakulchularp
    affiliation: Monash University
    address:
    - Faculty of Business and Economics
    - Melbourne, Australia
    orcid: 0009-0008-5638-7124
    email:  kanu0003@student.monash.edu
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: animbook-journal.bib

@@

# Explanation of the NY Times visualization

# Data

Diagram illustrating what data is expected, and how it is processed.

# Animation tools

Literature review of animation tools

<!-- To look for the flow between group, one of the most common tools we look at is sankey chart. It represent the movement of the values from one set to another. However, with the static sankey, the only information presented are what is the proportion of the movement, and which states the quantities move to, this often enough in explaining the flow and helps making the decision necessary. To present more information, color could be used to represent the demographic of the group. What if the information that are interesting lies in the times domain, how could the plot captured that information?

@@

The osiris data from Bureau van Dijk, contains an information on listed, and major unlisted/delisted companies across the world. This is one of an example of accounting data, where the objective is to observed the movement of the company between the quantile and how japan companies are ranked compared to others.-->

<!-- # Operation and data type abstraction

@@

The data set that will be used in this section and in all of the examples of this journal is collected from Bureau van Dijk. The data set contained 30,000 rows and 94 variable of information on listed, and major unlisted/delisted companies across the world. From the raw data, we are only interested in the ranking of the companies. The cleaned version of this data set is included in the package which only contained the relevant variables to reproduce the animated plot.
-->

# Visualization design

This explains how to get from data to the animations, including different sorts of plots.

# Software

## Installation

## Overview of functions

## Example usage

@@

<!-- # Package Usage

## Data preprocesing step-->

@@

# Application

## Accounting database: osiris

## Voter behavior

### 2023-10-02 animbook-journal.tex
structure of paper

% !TeX root = RJwrapper.tex
\title{animbook: An R Package for Visualize \ldots{}}
\author{by Krisanat Anukarnsakulchularp}

@@

\hypertarget{problem-and-data-characterization}{%
\section{Problem and data characterization}\label{problem-and-data-characterization}}

To look for the flow between group, one of the most common tools we look at is sankey chart. It represent the movement of the values from one set to another. However, with the static sankey, the only information presented are what is the proportion of the movement, and which states the quantities move to, this often enough in explaining the flow and helps making the decision necessary. To present more information, color could be used to represent the demographic of the group. What if the information that are interesting lies in the times domain, how could the plot captured that information?

!!general sankey plot and sankey with color

The technique that is created by Hans, Ola, and Anna Rosling in 2003 is called Gapminder Trendalyzer. Its add an additional dimensions which are the bubble size, animated over changes in a fourth dimension, time. The animation in this tools has created a new way for people to analyse and visualize the trend.

!!read effectiveness of animation in trend visualization, then add more information to above paragraph

The osiris data from Bureau van Dijk, contains an information on listed, and major unlisted/delisted companies across the world. This is one of an example of accounting data, where the objective is to observed the movement of the company between the quantile and how japan companies are ranked compared to others.

\hypertarget{operation-and-data-type-abstraction}{%
\section{Operation and data type abstraction}\label{operation-and-data-type-abstraction}}

\hypertarget{visualization-and-interaction-design}{%
\section{Visualization and interaction design}\label{visualization-and-interaction-design}}

\hypertarget{package-design}{%
\section{Package design}\label{package-design}}

@@

\hypertarget{package-usage}{%
\section{Package Usage}\label{package-usage}}

\hypertarget{data-preprocesing-step}{%
\subsection{Data preprocesing step}\label{data-preprocesing-step}}

@@

>>>>

% !TeX root = RJwrapper.tex
\title{animbook: Visualizing changes in performance measures and demographic affiliations using animation}

\author{by Krisanat Anukarnsakulchularp}

@@

\hypertarget{explanation-of-the-ny-times-visualization}{%
\section{Explanation of the NY Times visualization}\label{explanation-of-the-ny-times-visualization}}

\hypertarget{data}{%
\section{Data}\label{data}}

Diagram illustrating what data is expected, and how it is processed.

\hypertarget{animation-tools}{%
\section{Animation tools}\label{animation-tools}}

Literature review of animation tools

\hypertarget{visualization-design}{%
\section{Visualization design}\label{visualization-design}}

This explains how to get from data to the animations, including different sorts of plots.

\hypertarget{software}{%
\section{Software}\label{software}}

\hypertarget{installation}{%
\subsection{Installation}\label{installation}}

\hypertarget{overview-of-functions}{%
\subsection{Overview of functions}\label{overview-of-functions}}

\hypertarget{example-usage}{%
\subsection{Example usage}\label{example-usage}}

@@

@@

\hypertarget{application}{%
\section{Application}\label{application}}

\hypertarget{accounting-database-osiris}{%
\subsection{Accounting database: osiris}\label{accounting-database-osiris}}

\hypertarget{voter-behavior}{%
\subsection{Voter behavior}\label{voter-behavior}}
